\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors

### 2021-08-15 Draft/Manuscript.tex
edits

\leavevmode\hypertarget{ref-chamberlain2020}{}%
47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web. R package version 0.9.99}. (2020).

@@

\leavevmode\hypertarget{ref-santos2018}{}%
52. Santos, T., Diniz-Filho, J. A., e Luis, T. R., Bini, M. \& Santos, M. T. Package `PVR'. (2018).

@@

\leavevmode\hypertarget{ref-legendre2012}{}%
54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier, 2012).

@@

\leavevmode\hypertarget{ref-therneau2015}{}%
65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package `rpart'. \emph{Available online: cran. ma. ic. ac. uk/web/packages/rpart/rpart. pdf (accessed on 20 April 2016)} (2015).

\leavevmode\hypertarget{ref-milborrow2015}{}%
66. Milborrow, S. Rpart. Plot: Plot rpart Models. An Enhanced Version of plot. Rpart. \emph{R package version} \textbf{1}, (2015).

>>>>

\leavevmode\hypertarget{ref-chamberlain2020}{}%
47. Chamberlain, S. \emph{et al.} Taxize: Taxonomic information from around the web. R package version 0.9.99 (2020).~at \href{https://CRAN.R-project.org/package=taxize}{https://cran.r-project.org/package=taxize}.

@@

\leavevmode\hypertarget{ref-santos2018}{}%
52. Chamberlain, S. \emph{et al.} Package `PVR'. R package version 0.3 (2018).~at \href{https://CRAN.R-project.org/package=PVR}{https://cran.r-project.org/package=PVR}.

@@

\leavevmode\hypertarget{ref-legendre2012}{}%
54. Legendre, P. \& Legendre, L. \emph{Numerical ecology}. (Elsevier, Amsterdam, 2012).

@@

\leavevmode\hypertarget{ref-therneau2015}{}%
65. Therneau, T., Atkinson, B., Ripley, B. \& Ripley, M. B. Package `rpart'. R package version 4.1-15 (2015).~at \href{https://CRAN.R-project.org/package=rpart}{https://cran.r-project.org/package=rpart}.

\leavevmode\hypertarget{ref-milborrow2015}{}%
66. Milborrow, S. Rpart. Plot: Plot rpart Models. An Enhanced Version of plot. Rpart. R package version 3.0.9 (2015).~at \href{https://CRAN.R-project.org/package=rpart.plot}{https://cran.r-project.org/package=rpart.plot}.
